---
title: "Assignment5"
author: "Matt Rega"
date: "September 29, 2017"
output: html_document
---

##Number 1
#Import yob2016 and make readable/useable
```{r}
library(reshape2)
df<-read.table("yob2016.txt")
df<-colsplit(df$V1,";",names=c("First Name","Gender","Number of Children"))
```

#Display the summary and structure of df
```{r}
summary(df)
head(df,10)
```

#Find which name is misspelled
```{r}
df[grep('yyy',df$`First Name`),]
```

#Remove misspelled observation and save dataset to y2016
```{r}
y2016<-df[-212,]
```

##Number 2
#Import yob2015 and make readable/useable
```{r}
y2015<-read.table("yob2015.txt")
y2015<-colsplit(y2015$V1,",",names=c("First Name","Gender","Number of Children"))
```

#Display the last ten rows
```{r}
tail(y2015,10)
```
All ten entries are males and were used 5 times

#Merge y2016 and y2015 by first name and assign it to final. Only include names who have data for both years
```{r}
final<-merge(y2016,y2015,by="First Name")
head(final,10)
```

##Number 3
#Create a column that adds the amount for both years.
```{r}
name_total<-final$`Number of Children.x`+final$`Number of Children.y`
final<-cbind(final,name_total)
final<-final[,-2]
names(final)<-c("First Name","Number of Children 2016","Gender","Number of Children 2015","Number of Children Past Two Years")
final<-final[c("First Name","Gender","Number of Children 2015","Number of Children 2016","Number of Children Past Two Years")]
head(final,10)
```

#Sort the data by total. What are the top 10 most popular names?
```{r}
final<-final[order(-final$`Number of Children Past Two Years`),]
head(final,10)
```

#Omit boys names and give top 10 girl names and assign to object girl
```{r}
girl<-final[which(final$Gender=="F"),]
girl<-girl[order(-girl$`Number of Children Past Two Years`),]
head(girl,10)
```

#Export these ten names to a cvs without headers
```{r}
mydata<-head(girl,10)
mydata<-mydata[c("First Name","Number of Children Past Two Years")]
write.table(mydata,file="Baby_Names.csv",col.names = FALSE,row.names = FALSE,sep=",")
```