---
title: "Assignment 4"
author: "Matt Rega"
date: "September 22, 2017"
output: html_document
---

##Number 1
#Install the fivethirtyeight package
```{r}
library(fivethirtyeight)
#install.packages("fivethirtyeight")
#install.packages("devtools")
```

#Assign the eighteenth data set to the object df
```{r}
df<-college_recent_grads
```

#Write out the URL in a comment to the related news story
```{r}
vignette("fivethirtyeight",package = "fivethirtyeight")
```
http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/

#Using R command give the dimensions and column names of this data frame
```{r}
dim(df) #dimensions of data frame
names(df) #column names of data frame
```

##Number 2
#Give the column names of the data frame. Right after that, write one that counts the number of columns but not rows
```{r}
names(df) #names of columns
ncol(df) #number of columns
```

#Generate a count of each unique major_category in the data frame
```{r}
major_count<-as.data.frame(table(df$major_category))
```

#Make a bar graph of major category
```{r}
par(las=2)
barplot(major_count$Freq,main="Major Degree Areas",horiz=TRUE, col=2, xlab="Number of Students",names.arg = major_count$Var1)
```

#Write the data frame to a csv file
```{r}
write.csv(df,file="College Recent Grads")
```
##Number3
https://github.com/mrega1/SMU-MSDS